Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-10-30 manuscript/manuscript.tex
Edited speed comparison in manuscript

We have recorded the computation times for the gravity potential, the gradient component $g_z$ and the Marussi tensor component $g_{zz}$ generated by a single tesseroid model with homogeneous ($\Delta t_\text{homogeneous}$) and variable ($\Delta t_\text{variable}$) density at different heights. Then we plotted the ratio between these computation times (see Figure \ref{fig:speed-comparison}):

\begin{equation}
    \text{Computation Times Ratio} =
        \frac{\Delta t_\text{variable}}{\Delta t_\text{homogeneous}}
    \label{eq:computation-times-ratio}
\end{equation}

From these results we can conclude that the homogeneous density code is up to twice faster than the new variable density algorithm for lower heights. However, the computation times ratio gets lower at greater heights, due to the reduction of the divisions made by the adaptive discretization algorithm. In summary, the new variable density code is fast enough to perform the calculations of a real model in a few minutes. \todo{real, esta bien la expresion?}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/speed-comparison.pdf}
\caption{Computation times ratio between a single tesseroid model with variable and with homogeneous density at different heights, defined in equation \ref{eq:computation-times-ratio}.}
\label{fig:speed-comparison}
\end{figure}

>>>>

We have recorded the computation times for the gravity potential, the gradient component $g_z$ and the Marussi tensor component $g_{zz}$ generated by a single tesseroid model ($35$km of thickness) with homogeneous, linear and exponential density (with $b=50$km) at different heights. Then we calculated the ratio between these computation times:

\begin{equation}
    \text{Computation Times Ratio} =
        \frac{\Delta t_\text{variable}}{\Delta t_\text{homogeneous}},
    \label{eq:computation-times-ratio}
\end{equation}

\noindent where $\Delta t_\text{homogeneous}$ and $\Delta t_\text{variable}$ are the computation times corresponding to the homogeneous model and to the variable density ones (linear and exponential).

On Figures \ref{fig:speed-comparison}a and \ref{fig:speed-comparison}b we can see the results of these comparison.
In the linear density case the density-based discretization algorithm is not applied because the inequation \ref{eq:delta-density} is never satisfied.
For this reason, the homogeneous density model is up to 5 times faster than the variable density one in this case.
On the other hand, the density-based discretization algorithm makes the computation slower: up to 20 times slower than the homogeneous density code.
Nevertheless, this increase in the computation time pays off with a guarantee on its accuracy.

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/speed-comparison.pdf}
\caption{Computation time ratio between a single tesseroid model with variable and with homogeneous density at different heights (defined in equation \ref{eq:computation-times-ratio}) for (a) a linear and (b) an exponential density.}
\label{fig:speed-comparison}
\end{figure}
